A Study on Online Sequential Learning using Bandits

### 2017-12-23 synopsis/intro1.tex
Latest on 23/12/2017

In today's world, artificial intelligence has proved to be a game-changer in designing agents that interact with an evolving environment and make decisions on the fly. The main goal of artificial intelligence is to design artificial agents that make dynamic decisions in an evolving environment. In pursuit of these, the agent can be thought of as making a series of sequential decisions by interacting with the dynamic environment which provides it with some sort of feedback or reward after every decision which the agent incorporates into its decision-making strategy to formulate the next decision to be made. In its simplest form, this problem can be captured by the multi-armed bandit (MAB) model. Infact the MAB model can be considered as a single looping state when the agent after taking an action, and observing the reward transitions back to the same state. That single looping state consist of several finite number of actions which are called as arms.

	The name bandit originated from the concept of casino slot machine where there are levers which are termed as arms and the learner can pull one lever and observe the reward associated with that arm, which is sampled from a distribution associated with the specific arm. This game is repeated $T$ times and the goal of the learner is to maximize its profit by finding an action-selection strategy or policy that optimizes some long-term performance measure.

>>>>

In today's world, artificial intelligence has proved to be a game-changer in designing agents that interact with an evolving environment and make decisions on the fly. The main goal of artificial intelligence is to design artificial agents that make dynamic decisions in an evolving environment. In pursuit of these, the agent can be thought of as making a series of sequential decisions by interacting with the dynamic environment which provides it with some sort of feedback or reward after every decision which the agent incorporates into its decision-making strategy to formulate the next decision to be made. In its simplest form, this problem can be captured by the multi-armed bandit (MAB) model \citep{bertsekas1996neuro}, \citep{sutton1998reinforcement}.

	The name bandit originated from the concept of casino slot machine where there are levers which are termed as arms and the learner can pull one arm and observe the reward associated with that ar. This reward is sampled from a probability  distribution associated with that specific arm. This game is repeated $T$ times and the goal of the learner is to maximize its profit by finding an action-selection strategy or policy that optimizes some long-term performance measure.

	%Infact the MAB model can be considered as a single looping state when the agent after taking an action, and observing the reward transitions back to the same state. That single looping state consist of several finite number of actions which are called as arms.
